Rank Comparison

### 2023-11-09 Code/RankComparison.Rmd
removed some chunks to make it run faster

The code below performs two clustered Wilcox tests, the first one without using
exact = True, and the second one with exact = True and 10,000 random
permutations. The tests compare the times and group by the Stage of the
competition which in the data is coded as 1 if it was a national championship
and 2 if it was the world championships. The tests cluster by athlete, of which
for each dataset an integer from 1-11 is used (the values are not significant).
For more information about the "ds" method, please look at the Rank-based
Comparison subsection of the Methods section of the paper or at this link here:
https://www.jstatsoft.org/article/view/v096i06.  The second test also includes
exact = TRUE which is used when sample sizes are small (as they are in this
case), additionally the number of random permutations (B) is set to be 10,000.

@@

This is seeing what would happen if we remove prelims, the sample sizes in the
test become very small: 26 observations and 9 clusters.
```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022NoPrelims.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
                method = "ds", 
                exact = TRUE, B = 10000)
```

```{r}
women_data <- read.csv("../Data/WomenClusrank2019vs2022.csv")
colnames(women_data) <- c("Time", "Athlete", "Year")
```

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds", 
                exact = TRUE, B = 1000000)
```

>>>>

The code below performs two clustered Wilcox tests, the first one without using
exact = True, and the second one with exact = True and 1,000,000 random
permutations. The tests compare the times and group by the Stage of the
competition which in the data is coded as 1 if it was a national championship
and 2 if it was the world championships. The tests cluster by athlete, of which
for each dataset an integer from 1-11 is used (the values are not significant).
For more information about the "ds" method, please look at the Rank-based
Comparison subsection of the Methods section of the paper or at this link here:
https://www.jstatsoft.org/article/view/v096i06.  The second test also includes
exact = TRUE which is used when sample sizes are small (as they are in this
case), additionally the number of random permutations (B) is set to be 1,000,000.

@@

This is seeing what would happen if we remove prelims, the sample sizes in the
test become very small: 26 observations and 9 clusters.
```{r}
#nations_noprelim <- read.csv("../Data/Clusrank2019vs2022NoPrelims.csv")
#colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
#                method = "ds")
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
#                method = "ds", 
#                exact = TRUE, B = 10000)
```
